---
title: "Human Psychology of Conservation: Naming Patterns"
author: "Diego Ellis Soto"
date: "2025-07-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE
)
```

### Motivation

This analysis explores how researchers name tracked animals by combining:

Movebank metadata for animal movement studies

U.S. baby-name frequencies (1880–2017) via the babynames package

Key questions:

What proportion of tracked individuals receive “human” names?

How “creative” are the animal names (distance from common baby names)?

Where geographically are human-named animals most common?

Are there taxonomic biases (mammals vs. reptiles vs. others)?


```{r packs, echo=FALSE}
required_pkgs <- c(
  "move","dplyr","purrr","stringr","readr","sf",
  "rnaturalearth","rnaturalearthdata","babynames",
  "stringdist","ggplot2","wordcloud","tidyr","rgbif","ggrepel"
)
install.packages(setdiff(required_pkgs, installed.packages()[,"Package"]),
                 repos="https://cran.rstudio.com")
lapply(required_pkgs, library, character.only=TRUE)
```

